---
title: "p8105_hw1_sz2872"
author: "Shunyi Zhang"
date: "9/15/2020"
output: github_document
editor_options: 
  chunk_output_type: console
---

This is my solusion to hw1. 

```{r}
library(tidyverse)
library(tibble)
library(dplyr)
```

## Problem 1

Create a data frame with the specified elements. 

```{r creat_df}
prob1_df = 
  tibble(
    vec_num = rnorm(10),
    vec_log = vec_num > 0,
    vec_char = c("my", "cat", "names", "potato", "coke", "cola", "is", "a", "black", "kitty"),
    vec_factor = factor(c("small", "small", "small", "mid", "mid", "mid", "mid", "large", "large", "large"))
  )
```

Take the mean of each variable in my data frame.

```{r mean_df}
mean(pull(prob1_df, vec_num))
mean(pull(prob1_df, vec_log))
mean(pull(prob1_df, vec_char))
mean(pull(prob1_df, vec_factor))
```

I can take the mean for the numbers and logical but not for the character or factor. 

Convert vectors to numeric.

```{r convert_vec, eval = FALSE}
as.numeric(pull(prob1_df, vec_num))
as.numeric(pull(prob1_df, vec_log))
as.numeric(pull(prob1_df, vec_char))
as.numeric(pull(prob1_df, vec_factor))
```

R converts the logical vectors to numerical vectors. TRUE as 1. FALSE as 0. This is how r calculates the mean for the logical vectors in the previous step. 

R cannot convert character vectors to numerical vectors, thus cannot take the mean.

R assigns numerical value to to each category input of the factor vectors. The mean of this cant provide any information.  

Convert logical vectors.

```{r manipulate_vec}
as.numeric(pull(prob1_df, vec_log)) * pull(prob1_df, vec_num)
as.factor(pull(prob1_df, vec_log)) * pull(prob1_df, vec_num)
as.numeric(as.factor(pull(prob1_df, vec_log))) * pull(prob1_df, vec_num)
```

The result shows that numeric variables can be multiply by normal distributed variables, factor variables cannot. 

## Problem 2

Load the penguins dataset.

```{r load_package}
data("penguins", package = "palmerpenguins")
```

The penguins dataset contains `r ncol(penguins)` variables and `r nrow(penguins)` rows.

The **species** variable is a `r class(pull(penguins, species))` vector. The levels of **speices** are `r levels(pull(penguins, species))`. 

The **island** variable is a `r class(pull(penguins, island))` vector. The levels of **island** are `r levels(pull(penguins, island))`. 

The **bill_length_mm** variable is a `r class(pull(penguins, bill_length_mm))` vector. The range of **bill_length_mm** is `r range(pull(penguins, bill_length_mm), na.rm = TRUE)`. 

The **bill_depth_mm** variable is a `r class(pull(penguins, bill_depth_mm))` vector. The range of **bill_depth_mm** is `r range(pull(penguins, bill_depth_mm), na.rm = TRUE)`. 

The **flipper_length_mm** variable is a `r class(pull(penguins, flipper_length_mm))` vector. The range of **flipper_length_mm** is `r range(pull(penguins, flipper_length_mm), na.rm = TRUE)`. 

The **body_mass_g** variable is a `r class(pull(penguins, body_mass_g))` vector. The range of **body_mass_g** is `r range(pull(penguins, body_mass_g), na.rm = TRUE)`. 

The **sex** variable is a `r class(pull(penguins, sex))` vector. The levels of **sex** are `r levels(pull(penguins, sex))`. 

The **year** variable is a `r class(pull(penguins, year))` vector. The study is conducted from `r min(pull(penguins, year))` to `r max(pull(penguins, year))`. 

The variables in penguins are `r ls(penguins)`.

The mean of flipper length is `r round(mean(pull(penguins, flipper_length_mm), na.rm = TRUE),2)`.

Make a scatterplot relating the flipper length and the bill length. 

```{r make_scatterplot}
ggplot(data = penguins, 
       aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("scatter_plot.pdf", height = 6, width = 6)
```
